\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries

### 2014-11-05 HotOS'15/paper.tex
Done report for ashvin's course.

% --------------------------------------
\subsection{Proxy Memory and Tagged Reads}\label{sec:proxymem}

Proxy memory is a form of read-only shadow memory that summarizes or proxies actual memory access behavior. The key
idea  .... TODO!!

@@

\Toolname{} follows DataCollider's sampling based approach, but samples proxy memory instead of code \cite{DataCollider}.
\Toolname{} applies the roughly the following high-level algorithm to sample proxy memory and detect potential false sharing:
\begin{enumerate}
\item Choose a proxy memory address $P$ uniformly at random. Add a hardware watchpoint $w(P)$ to $P$.
\item If the watchpoint $w(P)$ is not triggered within $t$ units of time, then remove $w(P)$ and go to step (1).
\item If $w(P)$ is triggered for thread $T_i$ then pause $T_i$ for $t$ units of time. The hope is that within this
time slice, another thread, $T_j$ will be caught in the act of false sharing by triggering $w(P)$.
\item If $w(P)$ is not triggered again for another $t$ time units, then remove $w(P)$ and go to step (1).
\item If another thread $T_j$ triggers $w(P)$, then record stack traces for $T_i$ and $T_j$, and mark the associated program
counters of each of $T_i$ and $T_j$ as potentially having false sharing.
\item Go to step (1) to repeat the process for a new sample location.
\end{enumerate}

@@

% --------------------------------------------------------------------------------------
\section{Status}\label{sec:status}
\Toolname{} is being implemented using the Granary dynamic binary translator \cite{Granary}, as well as the address watchpoints
\cite{AddressWatchpoints} framework.

The following has been implemented:
% TODO...

% --------------------------------------------------------------------------------------
\section{Evaluation}\label{sec:evaluation}

% Answer the following questions:
%		1)	What are DataReactor's overheads over time?
%		2) 	How sensitive is DataReactor to different sampling rates?s
%		3)	How effective is DataReactor as discovering false sharing?
%		4)	Are the cases of detected false sharing high impact?

>>>>

% --------------------------------------
\subsection{Proxy Memory and Tagged Reads}\label{sec:proxymem}
Proxy memory is a form of variable-granularity shadow memory that proxies actual memory access behavior. The key
idea is to instrument all loads and stores in such a way that their load/store behavior is reflected in the shadow
memory in a way that can be externally observed. For example, one way to achieve this is to instrument every load
to read from shadow memory, every store to modify shadow memory, and trap loads and stores by adding hardware
watchpoints to shadow memory locations. Such heavyweight instrumentation would be inefficient, and so we apply
two optimizations: belief-based selective instrumentation, and tagged reads.

\paragraph{Selective Instrumentation}
The first optimization to proxy memory is to not instrument all code to operate on proxy memory. Initially, \Toolname{}
comprehensively instruments all code, thus incurring significant overheads. However, as beliefs about false sharing
are refined, less and less code is instrumented, thus allowing code to run faster when precision during identification of
potential false sharing is needed.

\paragraph{Tagged Reads}
The second optimization avoids the problem of introducing unnecessary cache coherency traffic by treating proxy memory
as read-only, and disambiguating the intention of an operation (load, store) by using a \emph{tagged read}. In our implementation,
a read operations (on the proxy memory) that intend to communicate loads (of actual memory) are distinguished from
read operations that intend to communicate a store by using different encodings of the logical \texttt{OR} instruction.

@@

\Toolname{} follows DataCollider's sampling based approach, but samples proxy memory instead of code \cite{DataCollider}.
\Toolname{} applies roughly the following high-level algorithm to sample proxy memory and detect potential false sharing:
\begin{enumerate}
\item Choose a proxy memory address $P$ uniformly at random. Add a hardware watchpoint $w(P)$ to $P$.
\item If the watchpoint $w(P)$ is not triggered within $t$ units of time, then remove $w(P)$ and go to step (1).
\item If $w(P)$ is triggered for thread $T_i$ then pause $T_i$ for $t$ units of time. The hope is that within this
time slice, another thread, $T_j$ will be caught in the act of contending on $P$ by triggering $w(P)$.
\item If $w(P)$ is not triggered again for another $t$ time units, then remove $w(P)$ and go to step (1).
\item If another thread $T_j$ triggers $w(P)$, then record stack traces for $T_i$ and $T_j$, and mark the associated program
counters of each of $T_i$ and $T_j$ as potentially having false sharing.
\item Go to step (1) to repeat the process for a new sample location.
\end{enumerate}

@@

% --------------------------------------------------------------------------------------
\section{Status}\label{sec:status}
\Toolname{} is being implemented using the Granary dynamic binary translator \cite{Granary} for the x86-64 architecture.

A limited form of proxy memory has been implemented. Work is progressing on making it possible to generically interpose
on memory allocators. Once this is done, the next step will be to work on the type analysis, as well as to associate typesets
with proxy memory locations. Code hotness analysis is expected to be an easy-to-do task. Concurrency analysis will be trickier.

Sampling and hardware watchpoint management will be orchestrated using GDB scripts.

% TODO...

% --------------------------------------------------------------------------------------
\section{Evaluation}\label{sec:evaluation}
Our evaluation aims to answer the following questions:
\begin{itemize}
\item What are \Toolname{}'s overheads? For example, what was the performance impact of the selective instrumentation
and tagged read optimizations?

\item How sensitive is \Toolname{} to different sampling rates, delays, and approaches? How does the thread
pause time during sampling affect our ability to detect false sharing? Can we quantify the benefits (if any) of
uniform heap sampling over na{\"i}ve heap sampling?

\item How effective is \Toolname{} at discovering false sharing? Is it able to distinguish between true sharing, false sharing,
and pseudo sharing?

\item How impactful are the instances of false sharing detected by \Toolname{}? Is code hotness a good metric for ranking
false sharing?
\end{itemize}

\subsection{Evaluation Challenges}
Granary is a medium weight DBT system, therefore its overheads will likely be significant. It is also new, and so no time has been
spent optimizing the code produced by Granary. Therefore, the overheads are not expected to be particularly good. The major
challenge will be convincing readers that:
\begin{enumerate}
\item Most of the analysis can be performed in a non-production environment, where we can claim that speed doesn't matter.
This will obviously be a contentious claim, because speed always matters, especially in false sharing detection. Here, I hope
that the belief propagation steps of the type and concurrency analysis stages will be beneficial in allaying those concerns.

\item The application of DataCollider to distinguish true and false sharing can be performed in production given the results of
all prior stages of the pipeline.
\end{enumerate}
